% !TEX TS-program = lualatex

\documentclass{tutodoc}

\usepackage{../preamble.cfg}

% DEBUG - START
%\geometry{showframe=true}
% DEBUG - END

\begin{document}

\phantomsection
\section*{\hfill Appendix 2 -- Palettes by category \hfill\null} \label{palette-categos}
\addcontentsline{toc}{section}{Appendix 2 -- Palettes by category}


\begin{tdocwarn}
    The palette names in this appendix are standard, but some \thisproj\ implementations add a specific prefix.
\end{tdocwarn}


\smallskip


\begin{tdocnote}[Qualitative and semantic palettes]
    The threshold of \palSemMaxSize\ colors has been established for qualitative and semantic palettes. The following lines outline the rationale for this limit.
    %
    \begin{itemize}
        \item In qualitative color palettes, each color represents a single data point or a group of data. Experience shows that about ten colors are more than enough.
     
        \item Semantic palettes associate a color with a specific context, such as warning levels (see the three frames in this document). Choosing \palSemMaxSize\ colors allows for \palSubSemSize\ different contexts, each with \palNbSemGrps\ sub-categories, for instance, a website where each context has specific states for 'visited', 'unvisited', or 'hovered' content.
    \end{itemize}
\end{tdocnote}


\smallskip


\begin{tdocimp}
    Categories were generated semi-automatically, followed by manual selection to obta
    in relevant choices.
\end{tdocimp}


% ------------------------------------------------ %
% -- BELOW, JUST TRANSLATE TITLES INSIDE BRACES -- %
% ------------------------------------------------ %

\foreach \nb/\kind/\title in {%
% -- FOREACH CATEGOS - AUTO - START -- %
  1/colorblind/{Colorblind palettes},%
  2/cyclic/{Cyclic palettes},%
  3/dark/{Dark palettes},%
  4/divergent/{Divergent palettes},%
  5/qualitative/{Qualitative palettes},%
  6/semantic/{Semantic palettes},%
  7/sequential/{Sequential palettes}%
% -- FOREACH CATEGOS - AUTO - END -- %
}{
  \ifthenelse{\nb = 1}{}{\newpage}

  \phantomsection
  \subsection*{\hfill\title\hfill\null}%
  \addcontentsline{toc}{subsection}{\texorpdfstring{\textbullet\,\title}{\title}}
  %
  \subimport{../../used-by-tools/}{catego-desc-\kind.latex}
  
  \begin{multicols*}{2}
    \subimport{../../../common/categos/}{\kind.latex}
  \end{multicols*}
}

\end{document}
