\documentclass{tutodoc}

\usepackage{../preamble.cfg}

% DEBUG - START
%\geometry{showframe=true}
% DEBUG - END


\begin{document}

\phantomsection\refstepcounter{appendixcnt}
\section*{\hfill Appendix \theappendixcnt\ -- Ignored palettes \hfill\null} \label{ignored-palettes}
\addcontentsline{toc}{section}{Appendix \theappendixcnt\ -- Ignored palettes}


\begin{tdocimp}
    The palette names in this appendix are standard, but some \thisproj\ implementations add a specific prefix.
\end{tdocimp}


% -------------------- %


\smallskip


\bgroup
  \def\title{Excluded by design} % To be translated.

  \phantomsection
  \subsection*{\hfill\title\hfill\null}%
  \addcontentsline{toc}{subsection}{\texorpdfstring{\textbullet\,\title}{\title}}
\egroup

The following palettes have been intentionally excluded. Please refer to the explanation below.

\subimport{../../used-by-tools/report/}{excluded-palettes.latex}


% -------------------- %


%\newpage


\bgroup
  \def\title{Rebuildable palettes} % To be translated.

  \phantomsection
  \subsection*{\hfill\title\hfill\null}%
  \addcontentsline{toc}{subsection}{\texorpdfstring{\textbullet\,\title}{\title}}
\egroup

The following palettes are excluded as sublists%
\footnote{
A palette is defined as a sublist if it is formed by removing colors while preserving the relative order of the remaining ones.
}
or shifts of existing ones, or due to direct or reversed duplication. Note that exact duplicates -- sharing both name and colors -- are omitted entirely. We identify relation between palettes using the following notations.

\medskip

\newcommand{\tabsymb}[1]{$\boxed{{#1}\vphantom{pM}}$}
\begin{tblr}{
  colspec = {*{6}{X[c]}},
  rows    = {m},
  cells   = {font = \small},
  row{2}  = {cmd = \tabsymb},
}
      Equality
    & Visually identical 
    & Reversal
    & Shifted 
    & Reversal and Shifted
    & Sublist 
    \\
      =
    & \cong
    & \rightleftharpoons
    & \ll
    & \revshiftarrows
    & \prec    
    \\
\end{tblr}

\medskip

In these cases, the rightmost palette is the one retained in \thisproj. For example, this table indicates that \tdoccodein{text}{YlOrRd} from \colorbrewer\ uses a sublist of colors from the \thisproj\ palette \tdoccodein{text}{YlOrRd}.

\subimport{../../../common/report/}{rebuildable-palettes.latex}


% -------------------- %


%\newpage


\bgroup
  \def\title{How to recover shifted/reversed palettes} % To be translated.

  \phantomsection
  \subsection*{\hfill\title\hfill\null}%
  \addcontentsline{toc}{subsection}{\texorpdfstring{\textbullet\,\title}{\title}}
\egroup

For the shifted and/or reversed palettes discussed in the previous section, we provide recovery methods. Below, we present pseudo-codes defining parameter values for use with the \thisproj\ palette API.

\subimport{../../../common/report/}{rebuild-palette-pseudo-codes.latex}

\end{document}
