\documentclass{tutodoc}

\usepackage{../preamble.cfg}

% DEBUG - START
%\geometry{showframe=true}
% DEBUG - END


\begin{document}

\phantomsection\refstepcounter{appendixcnt}
\def\title{Appendix \theappendixcnt\ -- \palsignored} % To be translated.
\section*{\hfill\title\hfill\null} \label{ignored-palettes}
\addcontentsline{toc}{section}{\title}


\begin{tdocimp}
    The palette names in this appendix are standard, but some \thisproj\ implementations add a specific prefix.
\end{tdocimp}


% -------------------- %


\smallskip


\bgroup
  \def\title{Excluded by design} % To be translated.

  \phantomsection
  \subsection*{\hfill\title\hfill\null}%
  \addcontentsline{toc}{subsection}{\texorpdfstring{\textbullet\,\title}{\title}}
\egroup

The following palettes have been intentionally excluded. Please refer to the explanation below.

\subimport{../../used-by-tools/report/}{excluded-palettes.latex}


% -------------------- %


%\newpage


\bgroup
  \phantomsection
  \subsection*{\hfill\palsunkept\hfill\null}%
  \addcontentsline{toc}{subsection}{\texorpdfstring{\textbullet\,\palsunkept}{\palsunkept}}
\egroup

The following types of palettes are unkept.
%
\begin{itemize}
    \item \textbf{Sublists:} formed by removing colors while preserving order.

    \item \textbf{Transformations:} reversals, shifts, or a combination of both.

    \item \textbf{Visual identical:} those indistinguishable to the naked eye.%
    \footnote{
        In these cases, the original palette is retained.
    }

    \item \textbf{Exact duplicates:} identical color arrays.
\end{itemize}
%
We identify relations between palettes using the following notations.

\smallskip

\begin{tblr}{
  colspec = {*{6}{X[c]}},
  rows    = {m},
  cells   = {font = \small},
  row{2}  = {cmd = \tabsymb},
}
      Duplicates
    & Visually identical 
    & Reversal
    & Shifted 
    & Shifted and Reversal
    & Sublist 
    \\
      =
    & \cong
    & \rightleftharpoons
    & \ll
    & \revshiftarrows
    & \prec    
    \\
\end{tblr}

\medskip

We list the unkept palettes below, omitting duplicates that share both name and colors. The rightmost palettes are those retained in \thisproj. For instance, the table shows that \matplotlib's \tdoccodein{text}{Gray} is the reversal of \thisproj's \tdoccodein{text}{Binary}.

\subimport{../../../common/report/}{unkept-palettes.latex}


%% -------------------- %
%
%
%%\newpage
%
%
%\bgroup
%  \phantomsection
%  \subsection*{\hfill\palsrebuild\hfill\null}%
%  \addcontentsline{toc}{subsection}{\texorpdfstring{\textbullet\,\palsrebuild}{\palsrebuild}}
%\egroup
%
%For the shifted and/or reversed palettes discussed in the previous section, we provide recovery methods. Below, we present pseudo-codes defining parameter values for use with the \thisproj\ palette API.
%
%\subimport{../../../common/report/}{rebuild-palette-pseudo-codes.latex}

\end{document}
