% !TEX TS-program = lualatex

\documentclass{tutodoc}

\usepackage{manual/preamble.cfg}


\begin{document}

\small


% -------------------- %


\begin{tdocbreak}
    \item Here are the breaking changes in the API.
    %
    \begin{itemize}
        \item Palette names use 'semantic' camelcase. For example, we use \tdoccodein{text}+PinkGrey+ and \tdoccodein{text}+BWR+ (Blue White Red) instead of \tdoccodein{text}+Pinkgrey+ and \tdoccodein{text}+Bwr+, but we keep \tdoccodein{text}+RdBu+ (RedBlue).


        \item \lua\ product: function \tdoccodein{lua}+getPal+ is now \tdoccodein{lua}+palCreateFromPal+. It expects a palette variable instead of a name alongside options.


        \item Contribution workflow has been fully changed (see below).


        \item No more same size for all the palettes (see below).


        \item  The categories have been fully changed (see below).
    \end{itemize}


    \item Manual: remove the cluster appendix.
\end{tdocbreak}


% -------------------- %


\begin{tdocnew}
    \item Here are the new API features.
    %
    \begin{itemize}
        \item 96 new palettes added.


        \item Multiple distribution formats are now available to meet various technical requirements.
        %
        \begin{itemize}
            \item High-fidelity (unmodified).

            \item Normalized (size $\leq$ \palMaxSemSize).

            \item One file per palette (nor more all palettes in one file).
        \end{itemize}


        \item Categories: the size palette is no longer used since the new API provides named categories. For example, a 3-color smooth palette can be now sequential, qualtitaive and/or semantic.


        \item Contribution workflow simplified significantly.
        %
        \begin{itemize}
            \item Data extraction and code generation are now streamlined by instantiating the \tdoccodein{python}+PaletteTransformer+ class, alongside palette and API builder functions.

            \item Monolithic or modular version can be omitted (\TeX\ can't build all the high-fidelity palettes at once).

            \item Standardized showcases now feature simplified graphics.
        \end{itemize}
    \end{itemize}
\end{tdocnew}


% -------------------- %


\begin{tdocupdate}
    \item Documentations explain the new API. Here are the changes made.
    %
    \begin{itemize}
        \item Contribution \tdoccodein{text}{README.md} files updated.


        \item Manual.
        %
        \begin{itemize}
            \item Added reference to \carbonplan.

            \item Added new category sections with a small description of their meaning.
        \end{itemize}
    \end{itemize}


    \item The projects listed below serves as a foundation.
    %
    \begin{itemize}
        \item \asymptote
        \item \carbonplan\      (new)
        \item \cartocolors
        \item \cmasher\         (new)
        \item \colorbrewer
        \item \colormaps\       (new, just for category automation)
        \item \matplotlib
        \item \nclcolortables\  (new, partially supported for now)
        \item \palettable
        \item \scicolmap
    \end{itemize}
\end{tdocupdate}

\end{document}
