% !TEX TS-program = lualatex

\documentclass{tutodoc}

\usepackage{../../preamble.cfg}


\begin{document}

\small


\begin{tdocbreak}
    \item \LUADRAW\ product becomes \lua\ product.


    \item \lua\ product: the dict-like variable \tdoccodein{lua}+palNames+ has been removed. Therefore, the responsibility of adding this specific variable will lie with \LUADRAW.
\end{tdocbreak}


\begin{tdocnew}
    \item New \css\ and \LaTeX\ products have been coded.


    \item The \palettable\ palettes have been added.


    \item Three semantic palettes \tdoccodein{text}+TdocBW+, \tdoccodein{text}+TdocCol+ and \tdoccodein{text}+TdocDark+ have been created to be used by the \tutodoc\ class (\LaTeX\ creation process used).


    \item Added an \thisdemo\ (the \css\ product showcase is used).
\end{tdocnew}


\begin{tdocupdate}
    \item Manual.
    %
    \begin{itemize}
        \item Added lists of renamed and removed palettes.

        \item Added two appendixes, one with all palettes grouped by user-friendly categories, and another showing similar palettes.

        \item Added explanations about the utility of palettes for non-designers.

        \item Added explanations about the minimal common optional sets of extra features implemented.
    \end{itemize}


    \item Better palette references.

    \item Better showcases.
    %
    \begin{itemize}
        \item Several category \pdf\ files are proposed (one \pdf\ per category and theme).

        \item 2D chart and Delaunay triangulation added.
    \end{itemize}
\end{tdocupdate}


\begin{tdocfix}
    \item \lua\ product: the \tdoccodein{text}+use-std.tex+ and \tdoccodein{text}+use-dark.tex+ codes have been fixed.
\end{tdocfix}

\end{document}
