\documentclass{tutodoc}

\usepackage{../preamble.cfg}


\begin{document}

\section{Where do the color palettes come from?}
\label{projects-used}

\thisproj\ includes some original creations, but most color palettes are derived from the projects listed below.
%
% ---------------------------------------- %
% -- JUST TRANSLATE THE ''XTRA'' TEXTS. -- %
% ---------------------------------------- %
%
% \def\fromcolormaps{palettes are extracted from \colormaps\ project}
\def\frompalettable{palettes are extracted from \palettable\ project}
%
\begin{multicols}{2}
\begin{itemize}
  \foreach \techno/\xtra in {%
    % -- A -- %
    \asymptote / {is used, but currently offers nothing beyond \matplotlib\ (despite different implementations)},%
    % -- C -- %
    \carbonplan  / {provides palettes designed for data visualization.},
    \cartocolors / \frompalettable,%
    \cmasher     / {provides palettes designed for data visualization.},
    \cmocean     / \frompalettable,%
    \colorbrewer / {provides professional color palettes for mapping and data visualization},%
    % \colorcet    / \fromcolormaps, %
    % -- L -- %
    \lightbartlein / \frompalettable,%
    % -- M -- %
    \matplotlib / {compiles color maps from diverse projects}, %
    \mycarta    / \frompalettable,%
    % -- P -- %
    \plotly / \frompalettable,%
    % -- S -- %
    \scicolmap / {provides palettes designed for colorblind accessibility}, %
    % \sciviz    / \fromcolormaps, %
    % -- T -- %
    \tableau / \frompalettable, %
    % -- W -- %
    \wesanderson / \frompalettable %
  }{%
    \item \techno\xtra.
  }
\end{itemize}
\end{multicols}


% -------------------- %


We retain only palettes that comply with the following rules.
%
\begin{itemize}
    \item \textbf{No repetition.}
    Unlike \matplotlib,%
    \footnote{
        Some \matplotlib\ palettes are duplicated, likely for historical reasons.
    }
    \thisproj\ use a one-to-one map from names to palettes.%
    \footnote{
        This does not preclude the existence of palettes with different names that are visually similar, or even looks identical. This is often justified by the number of colors used; a higher color depth helps prevent artifacts when generating high-resolution graphics.
    }


    \item \textbf{No reversed versions.}
    Unlike \matplotlib,%
    \footnote{
    	Most \matplotlib\ color maps have a reversed version named with the \tdoccodein{py}{_r} suffix, possibly for performance reasons.
    }
    \thisproj\ never includes reversed palettes as fixed data.


    \item \textbf{No shifted versions.}
    Unlike \colormaps,%
    \footnote{
    	These palettes use an integer suffix directly following the original palette name.
    }
    \thisproj\ never includes shifted palettes as fixed data (most implementations offer an API that enables this and other transformations through configurable parameters).


    \item \textbf{Reasonable palette sizes.} Palettes with more than \palMaxSize\ colors are ignored (e.g., \cmasher\ proposes 'neutral' palette, which consists of 2560 colors). 
    This avoids potential issues with certain technologies, such as \LaTeX, and frankly, offers a level of precision that is far beyond the needs of us mere mortals — or at least, those of us who aren't astronomers.
\end{itemize}


% -------------------- %


\begin{tdocnote}
    Adding new palettes to \thisproj\ is straightforward (no coding skills required).
    See section \ref{contrib-how-to-src-code} to get started.
\end{tdocnote}

\end{document}
