\documentclass{tutodoc}

\usepackage{../../contrib/translate/en/manual/preamble.cfg}

\makeatletter

\newcommand*\import@path@backup{}
\AddToHook{cmd/RobustInputMintedProcess/before}{%
  \let\import@path@backup\import@path%
  \def\import@path{}%
}
\AddToHook{cmd/RobustInputMintedProcess/after}{%
  \let\import@path\import@path@backup%
}

\makeatother

\usepackage[subpreambles = true]{standalone}


\begin{document}

\title{\thisproj*\ project}
\author{Christophe BAL}
\date{14 Mar 2026 -- Version 2.1.0}

\maketitle

\begin{abstract}
    The \thisproj\ project\,%
    \footnote{
        The name comes from \tdocquote{%
        \tdocprewhy{@.esthetic} \tdocprewhy{P.roducts} 
        for
        \tdocprewhy{R.epresenting} \tdocprewhy{I.nformative}
        \tdocprewhy{S.cientific} \tdocprewhy{M.aps}}.
        %
        This name is a double play on words:\kern3pt%
        \begin{enumerate*}[label={[\arabic*]}]
            \item a prism splits light into an informative spectrum, symbolizing how data are decomposed into meaningful color,
            and
            \item "@" read as "at" indicates where the light meets the prism to be broken down into an informative spectrum.
        \end{enumerate*}
    }
    provides \nbOfPals\ color palettes with native support for \css, \lua, and \LaTeX, to help you create expressive content

%    \smallskip
%
%    \noindent
%    \emph{\textbf{Remark :} this documentation is also available in <<DOC-LANGS>>.}
\end{abstract}

\tdocsep

{
\small

\bgroup
    \addtokomafont{subsection}{\centering}
    \subsection*{Last changes}
\egroup

% -------------------- %[version = 2.1.0, date = 2026-03-14]


\begin{tdocfix}
    \item Online demo: an auto-update script for the \tdoccodein{text}+HTML+, \tdoccodein{text}+CSS+ and \tdoccodein{text}+JavaScript+ codes was missing.
\end{tdocfix}


% -------------------- %


\begin{tdocbreak}
    \item Palette purification.
    %
    \begin{itemize}
        \item Deprecated sublist exclusion due to the high overhead of manual reconstruction:
        return of the palettes \tdoccodein{text}+BlueDarkOrange12+, \tdoccodein{text}+BlueOrange8+, and \tdoccodein{text}+BlueOrange10+.

        \item No more visual identical palettes (semi-automated process):
        \tdoccodein{text}+Cubehelix+ (\matplotlib) was removed, as it is visually identical to \tdoccodein{text}+Classic+ (\cubehelix).
    \end{itemize}
\end{tdocbreak}


% -------------------- %


\begin{tdocupdate}
    \item Manual.
    %
    \begin{itemize}
        \item The \tdoccodein{text}+Broc+, \tdoccodein{text}+GistRainbow+, and \tdoccodein{text}+Tofino+ palettes have been removed from the cyclic category.

        \item The \tdoccodein{text}+BlueDarkOrange12+, \tdoccodein{text}+BlueOrange8+, and \tdoccodein{text}+BlueOrange10+ palettes have been added to the sequential category.

        \item Added parameters allowing for the reconstruction of palettes omitted due to being shifted variants of existing ones.

        \item Added informative appendix describing subpalettes.
    \end{itemize}
\end{tdocupdate}
}

\newpage
\tableofcontents
\newpage

% -------------------- %

\subimport{../../contrib/translate/en/manual/about-this/}{motivations.tex}
\subimport{../../contrib/translate/en/manual/about-this/}{resources-used.tex}
\subimport{../../contrib/translate/en/manual/about-this/}{resources-curify.tex}
\subimport{../../contrib/translate/en/manual/about-this/}{reuse-from.tex}
\subimport{../../contrib/translate/en/manual/about-this/}{searching.tex}
\subimport{../../contrib/translate/en/manual/products/}{preamble.tex}
\subimport{../../contrib/translate/en/manual/products/}{css.tex}
\subimport{../../contrib/translate/en/manual/products/}{latex.tex}
\subimport{../../contrib/translate/en/manual/products/}{lua.tex}
\subimport{../../contrib/translate/en/manual/contribute/}{prologue.tex}
\subimport{../../contrib/translate/en/manual/contribute/}{translate.tex}
\subimport{../../contrib/translate/en/manual/contribute/}{src-code.tex}

% -------------------- %

\newpage
\section{History}

\small

% -------------------- %[version = 2.1.0, date = 2026-03-14]


\begin{tdocfix}
    \item Online demo: an auto-update script for the \tdoccodein{text}+HTML+, \tdoccodein{text}+CSS+ and \tdoccodein{text}+JavaScript+ codes was missing.
\end{tdocfix}


% -------------------- %


\begin{tdocbreak}
    \item Palette purification.
    %
    \begin{itemize}
        \item Deprecated sublist exclusion due to the high overhead of manual reconstruction:
        return of the palettes \tdoccodein{text}+BlueDarkOrange12+, \tdoccodein{text}+BlueOrange8+, and \tdoccodein{text}+BlueOrange10+.

        \item No more visual identical palettes (semi-automated process):
        \tdoccodein{text}+Cubehelix+ (\matplotlib) was removed, as it is visually identical to \tdoccodein{text}+Classic+ (\cubehelix).
    \end{itemize}
\end{tdocbreak}


% -------------------- %


\begin{tdocupdate}
    \item Manual.
    %
    \begin{itemize}
        \item The \tdoccodein{text}+Broc+, \tdoccodein{text}+GistRainbow+, and \tdoccodein{text}+Tofino+ palettes have been removed from the cyclic category.

        \item The \tdoccodein{text}+BlueDarkOrange12+, \tdoccodein{text}+BlueOrange8+, and \tdoccodein{text}+BlueOrange10+ palettes have been added to the sequential category.

        \item Added parameters allowing for the reconstruction of palettes omitted due to being shifted variants of existing ones.

        \item Added informative appendix describing subpalettes.
    \end{itemize}
\end{tdocupdate}

\tdocsep

% -------------------- %[version = 2.0.0, date = 2026-02-28]


\begin{tdocbreak}
    \item Here are the breaking changes in the API.
    %
    \begin{itemize}
        \item Palette names use 'semantic' camelcase. For example, we use \tdoccodein{text}+PinkGrey+ and \tdoccodein{text}+BWR+ (Blue White Red) instead of \tdoccodein{text}+Pinkgrey+ and \tdoccodein{text}+Bwr+, but we keep \tdoccodein{text}+RdBu+ (RedBlue).


        \item \lua\ product: function \tdoccodein{lua}+getPal+ is now \tdoccodein{lua}+palCreateFromPal+. It expects a palette variable alongside options.


        \item Contribution workflow has been fully changed (see below).


        \item No more same size for all the palettes (see below).


        \item No sublist or shifted palette.


        \item The categories have been fully changed (see below).
    \end{itemize}


    \item Manual.
    %
    \begin{itemize}
        \item Ignored and renamed palettes have been placed in dedicated appendices.

        \item Remove the cluster appendix.
    \end{itemize}
\end{tdocbreak}


% -------------------- %


\begin{tdocnew}
    \item Here are the new API features.
    %
    \begin{itemize}
        \item 95 new palettes added.


        \item Multiple distribution formats are now available to meet various technical requirements.
        %
        \begin{itemize}
            \item High-fidelity (unmodified) or normalized (size $\leq$ \palMaxSemSize).

            \item One file per palette (no more all palettes in a single file).
        \end{itemize}


        \item Categories: the size palette is no longer used since the new API provides named categories. For example, a 3-color smooth palette can be now sequential, qualtitative and/or semantic.


        \item Contribution workflow simplified significantly.
        %
        \begin{itemize}
            \item Data extraction and code generation are now streamlined by instantiating the \tdoccodein{python}+PaletteTransformer+ class, alongside palette and API builder functions.

            \item Standardized showcases now feature simplified graphics.
        \end{itemize}
    \end{itemize}
\end{tdocnew}


% -------------------- %


\begin{tdocupdate}
    \item Documentations explain the new API. Here are the changes made.
    %
    \begin{itemize}
        \item Contribution \tdoccodein{text}{README.md} files updated.


        \item Manual.
        %
        \begin{itemize}
            \item Added reference to \carbonplan.

            \item Added new category sections with a small description of their meaning.
        \end{itemize}
    \end{itemize}


    \item The projects listed below serve as a foundation.

    \bgroup
    \setlength{\multicolsep}{3pt}
    \begin{multicols}{2}
    \begin{itemize}
        \item \asymptote
        \item \carbonplan\      (new)
        \item \cartocolors
        \item \cmasher\         (new)
        \item \colorbrewer
        \item \colormaps\       (new, just for category automation)
        \item \matplotlib
        \item \nclcolortables\  (new, partially supported for now)
        \item \palettable
        \item \scicolmaps
    \end{itemize}
    \end{multicols}
    \egroup
\end{tdocupdate}

\tdocsep

% -------------------- %[version = 1.3.0, date = 2026-01-01]


\begin{tdocfix}
    \item \lua\ product: the \tdoccodein{text}+use-std.tex+ and \tdoccodein{text}+use-dark.tex+ codes have been fixed.
\end{tdocfix}


% -------------------- %


\begin{tdocbreak}
    \item \LUADRAW\ product becomes \lua\ product.


    \item \lua\ product: the dict-like variable \tdoccodein{lua}+palNames+ has been removed. Therefore, the responsibility of adding this specific variable will lie with \LUADRAW.
\end{tdocbreak}


% -------------------- %


\begin{tdocnew}
    \item New \css\ and \LaTeX\ products have been coded.


    \item The \palettable\ palettes have been added.


    \item Three semantic palettes \tdoccodein{text}+TdocBW+, \tdoccodein{text}+TdocCol+ and \tdoccodein{text}+TdocDark+ have been created to be used by the \tutodoc\ class (\LaTeX\ creation process used).


    \item Added an \thisdemo\ (the \css\ product showcase is used).
\end{tdocnew}


% -------------------- %


\begin{tdocupdate}
    \item Manual.
    %
    \begin{itemize}
        \item Added lists of renamed and removed palettes.

        \item Added two appendixes, one with all palettes grouped by user-friendly categories, and another showing similar palettes.

        \item Added explanations about the utility of palettes for non-designers.

        \item Added explanations about the minimal common optional sets of extra features implemented.
    \end{itemize}


    \item Better palette references.

    \item Better showcases.
    %
    \begin{itemize}
        \item Several category \pdf\ files are proposed (one \pdf\ per category and theme).

        \item 2D chart and Delaunay triangulation added.
    \end{itemize}
\end{tdocupdate}

\tdocsep

% -------------------- %[version = 1.2.1, date = 2025-11-09]


\begin{tdocfix}
    \item Equal palettes: the floating point equality uses now a correct tolerance.
\end{tdocfix}


% -------------------- %


\begin{tdocbreak}
    \item Palettes: the extra \tdoccodein{text}+Greys+ has been removed (it is equal to \tdoccodein{text}+Grays+).
\end{tdocbreak}


% -------------------- %


\begin{tdocnew}
    \item Similar palettes: two PDF files show similar palettes in standard and black modes (semi-automated process used).
\end{tdocnew}


% -------------------- %


\begin{tdocupdate}
    \item \LUADRAW\ product: the associative array \tdoccodein{lua}+palNames+ has been added for compatibility reasons with the \LUADRAW\ package.


    \item \tdoccodein{text}+BlindFish+ palette: the last color variation has been made smoother (\LUADRAW\ process used).
\end{tdocupdate}

\tdocsep

% -------------------- %[version = 1.2.0, date = 2025-10-29]


\begin{tdocbreak}
    \item Palettes: all final palettes now consist of 10 colors.


    \item \LUADRAW\ products: the \tdoccodein{lua}+getPal+ dictionary array has been converted into a function accepting string palette names (with or without \tdoccodein{lua}+pal+ prefix). See below.
\end{tdocbreak}


% -------------------- %


\begin{tdocnew}
    \item Palettes.
    %
    \begin{itemize}
        \item Added  \tdoccodein{text}+Lemon+ and \tdoccodein{text}+ShiftRainbow+ palettes (\LUADRAW\ creation process used).

        \item Added 37 palettes from the \scicolmaps\ project.
    \end{itemize}


    \item \LUADRAW\ product: accessing a palette and creating new ones can be made using the \tdoccodein{lua}+getPal+ function which has an optional argument \tdoccodein{lua}+options+ (dict-like array) with the following keys and their values.
    %
    \begin{itemize}
        \item \tdoccodein{lua}+extract+: a list of non-zero integers used to extract specific colors from the palette (the order is preserved).

        \item \tdoccodein{lua}+reverse+: a boolean value indicating whether to reverse the palette color order (\tdoccodein{lua}+false+ by default).

        \item \tdoccodein{lua}+shift+: an integer value for applying a circular color shift to the palette.
    \end{itemize}


    \item Documentations
    %
    \begin{itemize}
        \item Added English PDF manual.

        \item Showcase: two PDF files demonstrate the use of each palette (white and dark modes).
    \end{itemize}
\end{tdocnew}

\tdocsep

% -------------------- %[version = 1.1.0, date = 2025-10-14]


\begin{tdocbreak}
    \item Duplicate palettes and those that are reverse of others are ignored (strict equalities only).
\end{tdocbreak}


% -------------------- %


\begin{tdocnew}
    \item New palettes added: \tdoccodein{text}+BurningGrass+, \tdoccodein{text}+GeoRainbow+ and \tdoccodein{text}+PastelRainbow+ (\LUADRAW\ creation process used).

    \item The \LUADRAW\ palette product has a new dictionary like variable \tdoccodein{lua}{getPal} to access a palette using its name (as a string variable).
\end{tdocnew}


% -------------------- %


\begin{tdocupdate}
    \item Palette contributions: in the mandatory \verb+extend.py+ file, the \tdoccodein{py}{build_code} function must work with the dictionary of all the palettes, and manage a credit to the \thisproj\ project.
\end{tdocupdate}

\tdocsep

\tdocstartproj{First public version of the project.}\tdocversion{1.0.0}[2025-10-11]


% -------------------- %

\normalsize

\newpage
\subimport{../../contrib/translate/en/manual/appendixes/}{all-names.tex}
\newpage
\subimport{../../contrib/translate/en/manual/appendixes/}{renamed.tex}
\newpage
\subimport{../../contrib/translate/en/manual/appendixes/}{ignored.tex}
\newpage
\subimport{../../contrib/translate/en/manual/appendixes/}{subpals.tex}
\newpage
\subimport{../../contrib/translate/en/manual/appendixes/}{categos.tex}

\end{document}
